Bird beak's elaboration and innovation

### 2022-05-27 Analysis/03-Elaboration_innovation_analysis.Rmd
Update 03-Elaboration_innovation_analysis.Rmd

## Save all that as a list
save(ploting_data, file = "ploting_data.rda")

>>>>

## Getting the plotting data super_order_level
ploting_data_superorder <- list(
                     "median_elaborations" = apply(get.disparity(get.subsets(results$super_results_within$position, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median),
                     "median_innovations"  = apply(get.disparity(get.subsets(results$super_results_within$distance, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median),
                     "distances_to_centre" = get.disparity(dispRity(get.subsets(superorder_shapespace, subsets = "phylogeny"), metric = centroids, centroid = 0)),
                     "consensus_tree"      = tree)

## Getting the plotting data super_order_level
ploting_data_order <- list(
                     "median_elaborations" = apply(get.disparity(get.subsets(results$order_results_within$position, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median),
                     "median_innovations"  = apply(get.disparity(get.subsets(results$order_results_within$distance, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median),
                     "distances_to_centre" = get.disparity(dispRity(get.subsets(superorder_shapespace, subsets = "phylogeny"), metric = centroids, centroid = 0)),
                     "consensus_tree"      = tree)

## Save all that as a list
save(ploting_data, file = "../Data/Processed/ploting_data.rda")
save(ploting_data_superorder, file = "../Data/Processed/ploting_data_superorder.rda")
save(ploting_data_order, file = "../Data/Processed/ploting_data_order.rda")
